---
title: "R Notebook"
output: html_notebook
---

---
title: "R Notebook"
output: html_notebook
---

```{r}
# Tab = read.csv("/Users/sanaemessoudi/Desktop/DSMA/Project/Final_Datasets/Dataset_with_Cater_Latenight_Attire.csv")
Tab = read.csv("/Users/sanaemessoudi/Desktop/DSMA/Final_Project/2b) Data_Model_1/3b) Supervised_Data_No_Outliers.csv")

#library(readxl)
#Tab = read_excel("Dateiname.xlsx")
```

```{r}
summary(Tab)
```

```{r}
str(Tab)
```


```{r}
Tabelle = table(Tab$rating)
Tabelle
barplot(Tabelle, main = "" )
```
*According to the distribution of 0 and 1 it does not seem as if the dataset is imbalanced. To test this theory we calculate imbalance ratio, and Shannon Entropy in the following.*

```{r}
# Load necessary libraries (if needed)
if (!requireNamespace("dplyr", quietly = TRUE)) {
  install.packages("dplyr")
}
library(dplyr)

# Function to check for class imbalance
check_imbalance <- function(data, column) {
  # Calculate class distribution
  class_counts <- data %>%
    group_by(!!sym(column)) %>%
    summarize(count = n()) %>%
    ungroup()
  
  # Calculate proportions
  total <- sum(class_counts$count)
  proportions <- class_counts$count / total
  
  # Imbalance Ratio (IR)
  imbalance_ratio <- max(class_counts$count) / min(class_counts$count)
  
  # Shannon Entropy
  shannon_entropy <- -sum(proportions * log2(proportions))
  max_entropy <- log2(length(class_counts$count))
  entropy_ratio <- shannon_entropy / max_entropy
  
  # Decision and explanation
  if (imbalance_ratio > 1.5 || entropy_ratio < 0.8) {
    imbalance_statement <- paste(
      "The dataset is imbalanced. The imbalance ratio is",
      round(imbalance_ratio, 2),
      "and the Shannon Entropy ratio is",
      round(entropy_ratio, 2),
      "indicating a skew in class distribution."
    )
  } else {
    imbalance_statement <- paste(
      "The dataset is not significantly imbalanced. The imbalance ratio is",
      round(imbalance_ratio, 2),
      "and the Shannon Entropy ratio is",
      round(entropy_ratio, 2),
      "indicating a fairly balanced class distribution."
    )
  }
  
  # Output results
  print(class_counts)
  print(imbalance_statement)
}

# Example Usage
# Create a sample dataset
set.seed(42)
data <- data.frame(ratings = sample(c(0, 1), size = 4457, replace = TRUE, prob = c(0.55, 0.45)))

# Check for imbalance
check_imbalance(data, "ratings")

```



```{r}
Var = Tab$week_hours
boxplot(Var)
hist(Var)
summary(Var)
```

```{r}
Var = Tab$rating_stars
boxplot(Var)
hist(Var)
summary(Var)
```


```{r}
Var = Tab$rating_review_count
boxplot(Var)
hist(Var)
summary(Var)
```


```{r}
Var = Tab$rating_popularity
boxplot(Var)
hist(Var)
summary(Var)
```






```{r}
Tabelle = table(Tab$rating_price)
Tabelle
barplot(Tabelle, main = "" )
```
*Most restaurants offer meals at moderating price.*

```{r}
Tabelle = table(Tab$social_media)
Tabelle
barplot(Tabelle, main = "" )
```
*Most restaurants have at least one (1 block plus 2 block) social media account.*

```{r}
Tabelle = table(Tab$ambiance_intimate)
Tabelle
barplot(Tabelle, main = "" )
```
*Should not have a significant effect on rating judement since it is highly imbalanced. The model might rely more heavily on other, less imbalanced predictors.*

```{r}
Tabelle = table(Tab$ambiance_touristy)
Tabelle
barplot(Tabelle, main = "" )
```
*Should not have a significant effect on rating judement since it is highly imbalanced. The model might rely more heavily on other, less imbalanced predictors.*

```{r}
Tabelle = table(Tab$ambiance_hipster)
Tabelle
barplot(Tabelle, main = "" )
```
*Should not have a significant effect on rating judement since it is highly imbalanced. The model might rely more heavily on other, less imbalanced predictors.*

```{r}
Tabelle = table(Tab$ambiance_divey)
Tabelle
barplot(Tabelle, main = "" )
```
*Should not have a significant effect on rating judement since it is highly imbalanced. The model might rely more heavily on other, less imbalanced predictors.*

```{r}
Tabelle = table(Tab$ambiance_classy)
Tabelle
barplot(Tabelle, main = "" )
```


```{r}
Tabelle = table(Tab$ambiance_upscale)
Tabelle
barplot(Tabelle, main = "" )
```
*Should not have a significant effect on rating judement since it is highly imbalanced. The model might rely more heavily on other, less imbalanced predictors.*

```{r}
Tabelle = table(Tab$ambiance_casual)
Tabelle
barplot(Tabelle, main = "" )
```

```{r}
Tabelle = table(Tab$ambiance_trendy)
Tabelle
barplot(Tabelle, main = "" )
```
*Should not have a significant effect on rating judement since it is highly imbalanced. The model might rely more heavily on other, less imbalanced predictors.*

```{r}
Tabelle = table(Tab$ambiance_romantic)
Tabelle
barplot(Tabelle, main = "" )
```
*Should not have a significant effect on rating judement since it is highly imbalanced. The model might rely more heavily on other, less imbalanced predictors.*

```{r}
Tabelle = table(Tab$meals_breakfast)
Tabelle
barplot(Tabelle, main = "" )
```





```{r}
Tabelle = table(Tab$meals_brunch)
Tabelle
barplot(Tabelle, main = "" )
```


```{r}
Tabelle = table(Tab$meals_lunch)
Tabelle
barplot(Tabelle, main = "" )
```


```{r}
Tabelle = table(Tab$meals_dinner)
Tabelle
barplot(Tabelle, main = "" )
```


```{r}
Tabelle = table(Tab$meals_dessert)
Tabelle
barplot(Tabelle, main = "" )
```
*Should not have a significant effect on rating judement since it is highly imbalanced. The model might rely more heavily on other, less imbalanced predictors.*

```{r}
Tabelle = table(Tab$meals_latenight)
Tabelle
barplot(Tabelle, main = "" )
```
*Should not have a significant effect on rating judement since it is highly imbalanced. The model might rely more heavily on other, less imbalanced predictors.*

```{r}
Tabelle = table(Tab$attr_parking)
Tabelle
barplot(Tabelle, main = "" )
```

```{r}
Tabelle = table(Tab$attr_credit_cards)
Tabelle
barplot(Tabelle, main = "" )
```



```{r}
Tabelle = table(Tab$attr_outdoor_seating)
Tabelle
barplot(Tabelle, main = "" )
```

```{r}
Tabelle = table(Tab$attr_tv)
Tabelle
barplot(Tabelle, main = "" )
```

```{r}
Tabelle = table(Tab$reservations)
Tabelle
barplot(Tabelle, main = "" )
```

```{r}
Tabelle = table(Tab$service_table_service)
Tabelle
barplot(Tabelle, main = "" )
```

```{r}
Tabelle = table(Tab$service_good_for_kids)
Tabelle
barplot(Tabelle, main = "" )
```

```{r}
Tabelle = table(Tab$service_good_for_groups)
Tabelle
barplot(Tabelle, main = "" )
```

```{r}
Tabelle = table(Tab$collect_takeout)
Tabelle
barplot(Tabelle, main = "" )
```
*Should not have a significant effect on rating judement since it is highly imbalanced. The model might rely more heavily on other, less imbalanced predictors.*

```{r}
Tabelle = table(Tab$collect_delivery)
Tabelle
barplot(Tabelle, main = "" )
```

```{r}
Tabelle = table(Tab$attr_attire_casual)
Tabelle
barplot(Tabelle, main = "" )
```

```{r}
Tabelle = table(Tab$attr_attire_dressy)
Tabelle
barplot(Tabelle, main = "" )
```

```{r}
Tabelle = table(Tab$attr_wifi_free)
Tabelle
barplot(Tabelle, main = "" )
```

```{r}
Tabelle = table(Tab$attr_wifi_paid)
Tabelle
barplot(Tabelle, main = "" )
```

```{r}
Tabelle = table(Tab$info_state)
Tabelle
barplot(Tabelle, main = "" )
```

# Bivariate Analyse
```{r}
AVar = Tab$rating
UVar = Tab$week_hours
plot(AVar,UVar)
abline(lm(AVar~UVar))
```


```{r}
boxplot(Tab$week_hours~Tab$rating)
mean(Tab$week_hours[Tab$rating== 1])
mean(Tab$week_hours[Tab$rating== 0])
```

```{r}
boxplot(Tab$rating_stars~Tab$rating)
mean(Tab$rating_stars[Tab$rating== 1])
mean(Tab$rating_stars[Tab$rating== 0])
```

```{r}
boxplot(Tab$NumVar~Tab$rating)
mean(Tab$NumVar[Tab$rating== 1])
mean(Tab$NumVar[Tab$rating== 1])
```

```{r}
# Define the list of column names
columns <- c("week_hours", "rating_stars", "rating_review_count", "rating_popularity") # Replace with your column names

# Loop through each column name and perform the operations
for (col_name in columns) {
  cat("Analysis for:", col_name, "\n")
  
  # Dynamically create the boxplot
  boxplot(Tab[[col_name]] ~ Tab$rating, main = paste("Boxplot of", col_name, "by Rating"))
  
  # Calculate the means for each rating
  for (rating_value in unique(Tab$rating)) {
    mean_value <- mean(Tab[[col_name]][Tab$rating == rating_value], na.rm = TRUE)
    cat("Mean for rating", rating_value, ":", mean_value, "\n")
  }
  
  cat("\n") # Add spacing between analyses
}

```


```{r}
columns <- c(
    "rating_price",
    "social_media",
    "ambiance_intimate",
    "ambiance_touristy",
    "ambiance_hipster",
    "ambiance_divey",
    "ambiance_classy",
    "ambiance_upscale",
    "ambiance_casual",
    "ambiance_trendy",
    "ambiance_romantic",
    "meals_breakfast",
    "meals_brunch",
    "meals_lunch",
    "meals_dinner",
    "meals_dessert",
    "meals_latenight",
    "attr_parking",
    "attr_credit_cards",
    "attr_outdoor_seating",
    "attr_tv",
    "reservations",
    "service_table_service",
    "service_good_for_kids",
    "service_good_for_groups",
    "collect_takeout",
    "collect_delivery",
    "alcohol",
    "attr_attire_casual",
    "attr_attire_dressy",
    "attr_wifi_free",
    "attr_wifi_paid")

# Print the dynamically generated column names (optional)
cat("Dynamically detected columns:\n")

# Loop through each column and calculate the table
for (col_name in columns) {
  cat("\nAnalysis for:", col_name, "\n")
  
  # Dynamically create the table
  if (is.numeric(Tab[[col_name]]) || is.factor(Tab[[col_name]])) {
    # Only proceed for numeric or factor columns
    table_output <- table(Tab[[col_name]], Tab$rating)
    
    # Add labels to the axes and print
    cat("Contingency Table for", col_name, "vs Rating:\n")
    cat("Rows: Categories of", col_name, "\n")
    cat("Columns: Ratings\n\n")
    print(table_output)
  } else {
    cat("Skipping non-numeric/non-factor column:", col_name, "\n")
  }
}

```


```{r}
# Print the dynamically generated column names (optional)
cat("Dynamically detected columns:\n")
print(columns)

# Loop through each column and calculate the table and boxplot
for (col_name in columns) {
  cat("\nAnalysis for:", col_name, "\n")
  
  # Dynamically create the table (if numeric or factor)
  if (is.numeric(Tab[[col_name]]) || is.factor(Tab[[col_name]])) {
    table_output <- table(Tab[[col_name]], Tab$rating)
    
    # Print the table with labels
    cat("Contingency Table for", col_name, "vs rating:\n")
    print(table_output)
  } else {
    cat("Skipping non-numeric/non-factor column:", col_name, "\n")
  }
  
  # Generate boxplots for numeric columns
  if (is.numeric(Tab[[col_name]])) {
    boxplot(
      Tab[[col_name]] ~ Tab$rating,
      main = paste("Boxplot of", col_name, "by Rating"),
      xlab = "Rating",
      ylab = col_name,
      col = "lightblue"  # Optional: Add color for visualization
    )
  }
}
```

*Aussage Möglich: social media, *
*Keine Aussage Möglich: ambience intimate, ambience touristy, ambience hipster, ambience divey, ambience upscale, ambience trendy, ambience romantic, meals breakfast, meals brunch, meals dessert, meals late night, Credit card, good for kids, good for groups, takeout, casual attire, dressy attire, wi-Fi paid*
*Correlated with high ratings: ambience classy, *

```{r}
# Load necessary libraries
library(ggplot2)
library(patchwork)  # For combining plots

# Load your dataset
data <- read.csv("/Users/sanaemessoudi/Desktop/DSMA/Entire_Project/3) Analysis (Supervised ML)/2b) Imputed_Dataset_ML_Analysis.csv")
```


```{r}
# Define variable categories
binary_dependent_var <- "rating"  # Define your binary dependent variable
continuous_vars <- c("week_hours", "rating_stars", "rating_review_count", "rating_popularity", "visitors")
ordinal_vars <- c("rating_price", "social_media")
binary_vars <- c(
  "ambiance_intimate", "ambiance_touristy", "ambiance_hipster", "ambiance_divey", 
  "ambiance_classy", "ambiance_upscale", "ambiance_casual", "ambiance_trendy", 
  "ambiance_romantic", "meals_breakfast", "meals_brunch", "meals_lunch", 
  "meals_dinner", "meals_dessert", "attr_parking", "attr_credit_cards", 
  "attr_outdoor_seating", "attr_tv", "reservations", "service_good_for_kids", 
  "service_good_for_groups", "collect_takeout", "collect_delivery", "alcohol", 
  "attr_wifi_free", "attr_wifi_paid", "attr_attire_casual", "attr_attire_dressy", 
  "service_table_service", "meals_latenight"
)

# Visualize Binary Dependent Variable
dependent_plot <- ggplot(data, aes_string(x = binary_dependent_var)) +
  geom_bar(fill = "steelblue", color = "black", alpha = 0.7) +
  theme_minimal() +
  labs(title = paste("Distribution of", binary_dependent_var), x = binary_dependent_var, y = "Count")

# Create individual plots for continuous variables
continuous_plots <- lapply(continuous_vars, function(var) {
  ggplot(data, aes_string(x = var)) +
    geom_histogram(bins = 30, fill = "steelblue", color = "black", alpha = 0.7) +
    theme_minimal() +
    labs(title = paste("Distribution of", var), x = var, y = "Frequency")
})

# Create individual plots for ordinal variables
ordinal_plots <- lapply(ordinal_vars, function(var) {
  ggplot(data, aes_string(x = var)) +
    geom_bar(fill = "orange", color = "black", alpha = 0.7) +
    theme_minimal() +
    labs(title = paste("Distribution of", var), x = var, y = "Count")
})

# Create individual plots for binary variables
binary_plots <- lapply(binary_vars, function(var) {
  ggplot(data, aes_string(x = var)) +
    geom_bar(fill = "forestgreen", color = "black", alpha = 0.7) +
    theme_minimal() +
    labs(title = paste("Distribution of", var), x = var, y = "Count")
})

# Combine the plots
# Start with dependent variable plot
combined_plot <- (dependent_plot / wrap_plots(continuous_plots[1:4]) / wrap_plots(ordinal_plots[1:2]) / wrap_plots(binary_plots[1:6]))

# Display the combined plot
combined_plot

```


